---
title: "Basic exploratory analysis"
author: |
  | Camilo A. Ordóñez-Pinilla
  | camilo.ordonez@gmail.com
  

date: "09/28/2020"

output:

  html_document:
  
    theme: journal
    highlight: tango
---
### **Project 'Propuesta de comunicación pública basada en el análisis de la motivación para la adopción de las conductas de prevención en el contexto del COVID-19'**

### Github Link

RMarkdown code that generates this notebook is available to project members at  [github](https://github.com/caordonezp/project_ascofapsi_2020)

## Preliminars

As usual, we start setting up the working directory

```{r}
setwd ("E:/OTHER ACADEMICS/PROYECTOS COVID 19/PROYECTOS DATOS ASCOFAPSI/project_ascofapsi_2020")
```

Loading the required packages

```{r}

pacman::p_load(tidyverse, dplyr, summarytools, ggplot2, readxl, summarytools)
```


and uploading the data base in a new data frame called 'ascofapsi'

```{r}
ascofapsi <- read_excel("base de datos limpia.xlsx")
```

## Variables 

Variables were divided in three sets (see file 'variables selection'): predictors (demographics, costs and utilities, motives), mediators (personality and autoeficacy) and dependent measures (covid prevention behaviors).

## Descriptive summary

```{r}
print(dfSummary(ascofapsi, graph.magnif = 0.75), method = 'render')
```

* We have 926 observations of 118 variables.

* Variables about change: worsening of physic activity, sleep, economy, job, but improvement in family relationships and free time activities.

* Variables about covid prevention behaviors

  * High hand-washing, not face touching, social distance, quarantine, and social coregulation. 
  * Low in using gloves.
  * High levels of beliefs in being capable of maintaining the recommended behaviors.
  
* Variables about motives
  * More agreement in self and social welfare. (utilitarian)
  * More symmetry in social and legal motives.
  
* Variables about utility
  * People belief that prevention behaviors are useful but using gloves (the one that people are not performing)
  
* People recognize that coregulation is useful but it has low implementation

* Sample
  * Professional
  * More women than men

## Some graphs

- As an example, we have more women (1) than men, and this is presented in how using mask is distributed by gender (differences by gender are not well represented since the unbalance)

```{r}
  qplot (r_usotapabocas, data=ascofapsi, fill = as.factor(genero))
```
```{r}
 qplot (as.factor(motiv_evitarcontagio_yo), r_usotapabocas, data=ascofapsi, geom = "boxplot")
```
```{r}
 qplot (as.factor(motiv_evitarcontagio_otro), r_usotapabocas, data=ascofapsi, geom = "boxplot")
```

```{r}
qplot (as.factor(motiv_evitarconflicto), r_usotapabocas, data=ascofapsi, geom = "boxplot")
```
```{r}
 qplot (as.factor(motiv_evitarlegales), r_usotapabocas, data=ascofapsi, geom = "boxplot")
```
```{r}
qplot (as.factor(motiv_evitarlegales), as.factor(r_usotapabocas), data = ascofapsi, facets = .~genero)
```
```{r}
 qplot (r_usotapabocas, data=ascofapsi, fill = as.factor(motiv_evitarlegales))
```


```{r}

qplot (r_usotapabocas, data=ascofapsi, fill = as.factor(motiv_evitarlegales))

``` 
```{r}
qplot (r_usotapabocas, data=ascofapsi, fill = as.factor(motiv_evitarconflicto))
```
```{r}
cor.test(ascofapsi$r_usotapabocas, ascofapsi$r_lavadomanos)
```
```{r}
 plot (ascofapsi$r_usotapabocas, ascofapsi$i_usotapabocas)
```
Create a data frame for the relation between intentions and actions
```{r}
intentions_actions <- (select (ascofapsi, i_usotapabocas:i_pedir_cprev, r_usotapabocas: r_pedir_cprev))
```

```{r}
cor(intentions_actions                                                                                                                                                               )
```

